---
title: "NAAZ PARVAZ"
---

# About me

> Hi there! I’m Naaz, a professional who loves exploring how data, creativity and storytelling come together to drive impactful strategies. I have a background in **marketing** and after 3 years of working on the creative side, I decided that I wanted to transition into a more technical role. As a result, I'm now pursuing a **Masters in AI and Business Analytics\* from Zicklin School of Business at Baruch College**.

```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.74028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "I am a Master's student at <b>Baruch College</b>!")
```

```{r}
#| include: false
1+1
```

------------------------------------------------------------------------

> *Connect with me on [LinkedIn!](https://www.linkedin.com/in/naaz-parvaz/)*

Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`
